%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]
\usepackage{import}
\usepackage{fontawesome}
%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Miguel} \headerlastnamestyle{Azeredo Santos} \\
	
	\headersocialstyle{ {\faEnvelope\ miguelazeredomals@gmail.com} | {\faGithub\ github.com/xtravaganzaa} | {\faLinkedinSquare\ linkedin.com/in/miguel-azeredo-santos-5a2971117/} }
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Education}
\begin{cventries}
	\cventry
	{Graduation in computer engineering}
	{Higher Institute of Engineering of Porto (ISEP)}
	{Porto, Portugal}
	{2016 - 2019}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Internship}
	{3C TechLab}
	{Porto, Portugal}
	{March 2019 - September 2019}
	{\begin{cvitems}
		\item {Designed and implemented a software solution for handling payment terminal screens.}
		\item {A translation API is used to convert screens details to other languages and Git version control is implemented in the application itself.}
	\end{cvitems}}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5mm}
\cvsection{Projects}
\begin{cventries}
 	\cventry
	{Simple software that takes advantage of AHP and Topsis multi-criteria decision analysis methods.}
	{Multi-criteria analysis methods}
	{Java}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Basic concepts of analysis, modelling and object oriented programming 
	that gives a solution to support organization and event management}
	{Event management application}
	{Java, XML}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Study on the energy consumption in road
	transformation, through a simulation of a road network that
	applied classical mechanics and fluids laws. Based on the CDIO approach.}
	{Road network simulator}
	{Java, PL/SQL, XML}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Implementation of a web version of Cleansheets, a Desktop worksheet application available at Bitbucket,
	very similar to Microsoft Excel. Also including online chat between registered users.}
	{Web version of Cleansheets}
	{ANTLR, Java, JS, XML}
	{}
	{}

	\vspace{-5mm}
	\cventry
	{Online application that supports closets personalization and order.
	 The product can be visualized in 3D before ordering and the shortest path 
	 between factory-client is calculated. All data is handled and kept private using GDPR rules.}
	{Closets conception and order application}
	{C\#, Angular, Node.js, PROLOG, JavaScript, TypeScript, Three.js}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Skills}
\begin{cventries}
	\vspace{-2mm}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming Languages:  & {\skill{ Java, JavaScript, C\#, PROLOG }} \\
		Technology Used:  & {\skill{ Angular, Node.js, .NET Core, Jira, Git, SonarQube, Jenkins, Oracle, Maven}} \\
		Spoken Languages:  & {\skill{ English, Portuguese, French, Spanish}} \\
		Soft Skills:  & {\skill{ Team work, Self-motivation, Creativity, Good communication}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extra Curricular Activity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Extra Curricular Activity}
\begin{cvhonors}
	\cvhonor
	{GAME-A-THON – ISMAI Legends 2018}
	{Team of 5 making a game in 48h using Unity}
	{Maia, Portugal}
	{June 2018}
	\cvhonor
	{Mad Game Jam – ESMAD}
	{Team of 5 making a game in 48h using Phaser 3}
	{Vila de Conde, Portugal}
	{February 2019}
	\cvhonor
	{Interrail in Italy | Czech Republic | Austria | Germany | Slovenia}
	{Went on an adventure alone}
	{Europe}
	{August 2018}
\end{cvhonors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hobbies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Hobbies}
\begin{itemize}
	\item {Piano | Karaté | Video making \& editing} 
\end{itemize}
\end{document}